### 2016-06-07 targetDP/doc/examples.tex

\begin{figure}[h]
\begin{lstlisting}
__targetEntry__ void scale(double* t_field) { (*@\label{example:scalekernel:targetEntry}@*)

>>>>

\begin{figure}[h]
\begin{lstlisting}

//declare constant variable
__targetConst__ double t_a; (*@\label{example:scalekernel:targetConst}@*)

__targetEntry__ void scale(double* t_field) { (*@\label{example:scalekernel:targetEntry}@*)
